---
title: "Assignment_4"
author: "Vishnu Prasanth Reddy Patur"
date: "9/25/2019"
---


#### Loading Dataset
```{r message=FALSE, message=FALSE,warning=FALSE}

library(dplyr)
library(knitr)
setwd('C:/Users/vipra/Desktop/MSDA/STA6714_Data_Preperation/Assignments/Ass_4')
data_set<-read.csv('Malware_train_s.csv')

```


#### Cleaning dataset
```{r }
#Data CLeaning
data_set$Census_ChassisTypeName<-as.character(data_set$Census_ChassisTypeName)
data_set$Census_ChassisTypeName[data_set$Census_ChassisTypeName==""]<-'Missing'
data_set$Census_ChassisTypeName[data_set$Census_ChassisTypeName=='UNKNOWN']<-'Unknown'
data_set$Census_ChassisTypeName<-as.factor(data_set$Census_ChassisTypeName)


data_set$Census_FirmwareManufacturerIdentifier<-as.character(data_set$Census_FirmwareManufacturerIdentifier)
data_set$Census_FirmwareManufacturerIdentifier[data_set$Census_FirmwareManufacturerIdentifier=='.']<-'Unknown'
data_set$Census_FirmwareManufacturerIdentifier<-as.factor(data_set$Census_FirmwareManufacturerIdentifier)

data_set1<-subset(data_set,select = c('AppVersion','Census_ActivationChannel','Census_ChassisTypeName','Census_DeviceFamily','Census_FirmwareManufacturerIdentifier'))
```




#### Function for producing SMOOTH LOGIT TABL, input- Dataset, Target Variable, Treshold, CategoricalVariable and Smoothing Factor
```{r }
#Function
smoothed_function<-function(dataset,target_variable,treshold,CategoricalVariable,smoothfactor){
a<-table(dataset[CategoricalVariable])
a<-as.data.frame(a)

yes<-subset(dataset,dataset[target_variable]==1)
no<-subset(dataset,dataset[target_variable]==0)

a_yes<-table(yes[CategoricalVariable])
a_yes<-as.data.frame(a_yes)

a$YES_freq<-a_yes$Freq
a$NO_freq<-a$Freq-a$YES

if (treshold>0){
  a1<-subset(a,a$Freq>=treshold)
  f_no=nrow(a)-nrow(a1)
  a<-a[order(a$Freq),]
  sum_f<-sum(a$Freq[1:f_no])
  sum_y<-sum(a$YES_freq[1:f_no])
  sum_n<-sum(a$NO_freq[1:f_no])
  new<-data.frame(Var1='New Category',Freq=sum_f,YES_freq=sum_y,NO_freq=sum_n)
  a<-rbind(a1,new)
}
a$Prop_yes=a$YES/a$Freq
a$prop_no=1-a$Prop_yes

a$smoot_logit <-log((a$YES_freq+a$Prop_yes*smoothfactor)/(a$NO_freq+a$prop_no*smoothfactor))
return(a)
}


```




**SmoothLogit for `AppVersion` treshold=35, smoothing factor=50**
```{r }

appversion_smoothed<-smoothed_function(data_set,'HasDetections',35,'AppVersion',50)
kable(appversion_smoothed)

```


**SmoothLogit for `Census_ChassisTypeName` treshold=70, smoothingfactor=100**
```{r }

Census_ChassisTypeName_smothed<-smoothed_function(data_set,'HasDetections',70,'Census_ChassisTypeName',100)

kable(Census_ChassisTypeName_smothed)

```



**SmoothLogit for `Census_ActivationChannel` treshold=0, smoothingfactor=100**
```{r }

Census_ActivationChannel_smothed<-smoothed_function(data_set,'HasDetections',0,'Census_ActivationChannel',100)
kable(Census_ActivationChannel_smothed)

```


**SmoothLogit for `Census_DeviceFamily` treshold=0, smoothingfactor=100**

```{r }

Census_DeviceFamily_smothed<-smoothed_function(data_set,'HasDetections',0,'Census_DeviceFamily',100)
kable(Census_DeviceFamily_smothed)
```


**SmoothLogit for `Census_FirmwareManufacturerIdentifier` treshold=700, smoothingfactor=50**
```{r }

Census_FirmwareManufacturerIdentifier_smothed<-smoothed_function(data_set,'HasDetections',0,'Census_FirmwareManufacturerIdentifier',50)

kable(head(Census_FirmwareManufacturerIdentifier_smothed,70))


```


# 50 bservations of input dataset with smooth logit
```{r}
#appending smoothed logit to input dataset provided treshold
appversion_smoothed$smoothAppversion<-appversion_smoothed$smoot_logit
Census_ChassisTypeName_smothed$smoothcensusChasistyp<-Census_ChassisTypeName_smothed$smoot_logit
Census_ActivationChannel_smothed$SmoothACTVTCHNL<-Census_ActivationChannel_smothed$smoot_logit
Census_DeviceFamily_smothed$smoothDeviceFmly<-Census_DeviceFamily_smothed$smoot_logit
Census_FirmwareManufacturerIdentifier_smothed$smoothfirmware<-Census_FirmwareManufacturerIdentifier_smothed$smoot_logit

smoothed_data_set<- merge(data_set1,subset(appversion_smoothed,select = c('Var1','smoothAppversion')),by.x = 'AppVersion',by.y = 'Var1',all.x = TRUE)

smoothed_data_set<- merge(smoothed_data_set,subset(Census_ChassisTypeName_smothed,select = c('Var1','smoothcensusChasistyp')),by.x = 'Census_ChassisTypeName',by.y = 'Var1',all.x = TRUE)

smoothed_data_set<- merge(smoothed_data_set,subset(Census_ActivationChannel_smothed,select = c('Var1','SmoothACTVTCHNL')),by.x = 'Census_ActivationChannel',by.y = 'Var1',all.x = TRUE)


smoothed_data_set<- merge(smoothed_data_set,subset(Census_DeviceFamily_smothed,select = c('Var1','smoothDeviceFmly')),by.x = 'Census_DeviceFamily',by.y = 'Var1',all.x = TRUE)

smoothed_data_set<- merge(smoothed_data_set,subset(Census_FirmwareManufacturerIdentifier_smothed,select = c('Var1','smoothfirmware')),by.x = 'Census_FirmwareManufacturerIdentifier',by.y = 'Var1',all.x = TRUE)



kable(head(smoothed_data_set,50))

```

